Differential invariant signatures for planar Lie group transformations of images

### 2021-08-09 paper/newpaper.tex
Started on revisions

\section{Introduction}
The appearance of a fixed object in a set of images can vary markedly depending upon such variables as pose and position relative to the camera, even though the object itself does not change. This is even more marked in scenes that consist of multiple objects at different distances and orientations to the camera against a fixed background. The appearance of each individual object will then vary independently as a constant camera motion or other such transformation is applied. Typically the individual transformations will appear as the action of an element of a planar Lie group, for example the affine, or projective groups, or an angle-preserving transformation from the conformal group, depending upon the camera model.

@@

Tables~\ref{tab:transvectants1} and~\ref{tab:transvectants2} shows all possible non-zero partial
transvectants of $A_2$ up to weight $4$ that can be generated in this way.

@@

The action of the affine group $A(2)$ arises in images as the motion of
planar objects in images taken from a distant camera. Recall that
because of the subgroup relationship, invariants of $A(2)$ are automatically invariants
of $SA(2)$, but not necessarily vice versa. Any of the partial
transvectants found in Tables~\ref{tab:transvectants1}
and~\ref{tab:transvectants2} are relative invariants of $SA(2)$ (as the determinant
is $1$). Hence, we can form a signature for $SA(2)$ by choosing any combination of
partial transvectants. We choose a signature with three components so that
it can be visualised as a three-dimensional surface; note that this will
not be complete and may well have a very large bad set. For example, we can
choose the function value together with $C$ and $D$ from Eq.~\eqref{eq:cde}
to form the signature:

@@

A moving frame is a mapping into a group $\mathcal{G}$ that provides a frame of reference along a manifold.  It was extended by~\citet{Cartan35} to the `method of moving frames'. If the group $\mathcal{G}$ is a Lie group then it has a homogeneous space and a frame of reference can be applied on the manifold structure of the group. Considering the actions of such a transformation group enables the identification of invariants to that group since it defines a $\mathcal{G}$-equivariant mapping. A (right-) moving frame is a smooth $\mathcal{G}$-equivariant map $\rho : \mathcal{M} \to \mathcal{G}$ such that $\rho (g \cdot z) = \rho(z) \cdot g^{-1}$, where $z \in J^d$. It is necessary~\citep{Olver2013} for the group act freely. This means that the group action needs to be extended to the entire jet space of derivatives up to order $d$ by implicit differentiation of the group action, a process known as prolongation.

>>>>

\section{Introduction}
The appearance of a fixed object in a set of images can vary markedly depending upon such variables as pose and position relative to the camera, even though the object itself does not change. This is even more marked in scenes that consist of multiple objects at different distances and orientations to the camera against a fixed background. The appearance of each individual object will then chnge in different ways as a constant camera motion or other such transformation is applied. Typically the individual transformations will appear as the action of an element of a planar Lie group, for example the affine, or projective groups, or an angle-preserving transformation from the conformal group, depending upon the camera model.

@@

Tables~\ref{tab:transvectants1} and~\ref{tab:transvectants2} show all possible non-zero partial
transvectants of $A_2$ up to weight $4$ that can be generated in this way.

@@

The action of the affine group $A(2)$ arises in images as the motion of planar objects in images taken from a distant camera. Because $SA(2)$ is a subgroup of $A(2)$, any invariant of $A(2)$ is also an invariant of $SA(2)$, but not necessarily vice-versa. Any of the partial transvectants found in Tables~\ref{tab:transvectants1} and~\ref{tab:transvectants2} are invariants of $SA(2)$ as the determinant is $1$. Hence, we can form a signature for $SA(2)$ by choosing any combination of partial transvectants. We choose a signature with three components so that it can be visualised as a three-dimensional surface; note that this will not be complete and may well have a very large bad set. For example, we can choose the function value together with $C$ and $D$ from Eq.~\eqref{eq:cde} to form the signature:

@@

A moving frame is a mapping into a group $\mathcal{G}$ that provides a frame of reference along a manifold.  It was extended by~\citet{Cartan35} to the `method of moving frames'. If the group $\mathcal{G}$ is a Lie group then it has a homogeneous space and a frame of reference can be applied on the manifold structure of the group. Considering the actions of such a transformation group enables the identification of invariants to that group since it defines a $\mathcal{G}$-equivariant mapping. A (right-) moving frame is a smooth $\mathcal{G}$-equivariant map $\rho : \mathcal{M} \to \mathcal{G}$ such that $\rho (g \cdot z) = \rho(z) \cdot g^{-1}$, where $z \in J^d$ and where $\cdot$ denotes the group operation of $\mathcal{G}$. It is necessary~\citep{Olver2013} for the group to act freely. This means that the group action needs to be extended to the entire jet space of derivatives up to order $d$ by implicit differentiation of the group action, a process known as prolongation.
